A Hitchhiker's Guide to Reproducible Research in R

### 2021-06-29 manuscript.Rmd
explain the autogenerated Dockerfile

>>>>

The the last Docker, `.repro/Dockerfile_packages`, should not be manually changed.
`repro::automate()` gathers all packages from all `.Rmd` files and figures out if they should be installed from CRAN or GitHub.
`repro::automate()` also simply combines the three Dockerfiles and saves the result into the main `Dockerfile` at the top level of the project.
The seperation into several Dockerfiles is only to provide a clear seperation between automatically generated parts and manually altered parts of the Dockerfile.
However, Docker requires in the end the one Dockerfile that `repro::automate()` creates from them.
